Supplement to ``{\mytitle}''

### 2022-12-15 si/si.Rnw
re-estimating model3 in SI for reproducibility

# Set Run Level for debug, timing, and full computation
RUN_LEVEL = 2

@@

# TODO: replace with bake
haiti3_orig_fit <- readRDS(save_file)

# haiti3_orig_fit <- bake(
#   file = save_file, {
#     fit_coupled_haiti3(
#       nsearches = N_SEARCHES,
#       search1 = SEARCH1,
#       search2 = SEARCH2,
#       search3 = SEARCH3,
#       search_rho = FALSE,
#       search_gamma = FALSE,
#       ncores = cores
#     )
#   }
# )

>>>>

@@

# TODO: replace with bake
# haiti3_orig_fit <- readRDS(save_file)

haiti3_orig_fit <- bake(
  file = save_file, {
    fit_coupled_haiti3(
      nsearches = N_SEARCHES,
      search1 = SEARCH1,
      search2 = SEARCH2,
      search3 = SEARCH3,
      search_rho = FALSE,
      search_gamma = FALSE,
      ncores = cores
    )
  }
)
